Databrary: Enabling sharing and reuse of research video

### 2015-04-22 jcdl-15/demo.tex
add permissions to front page

\documentclass{sig-alternate}

>>>>

\documentclass{sig-alternate-2013}

\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice%
\let\confname\myconfname%

\permission{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the Owner/Author.
Copyright is held by the owner/author(s).}
\conferenceinfo{JCDL'15,}{June 21--25, 2015, Knoxville, Tennessee, USA.}
\copyrightetc{ACM \the\acmcopyr}
\crdata{978-1-4503-3594-2/15/06. \\
http://dx.doi.org/10.1145/2756406.2756951}

\clubpenalty=10000
\widowpenalty = 10000
